---
title: "Striatal Network Dynamics are Associated with Reinforcement Learning"
subtitle: "Models"
author: "Raphael Gerraty"
output: pdf_document
---


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(reshape2)
library(lme4)
library(rstanarm)
library(brms)
library(lattice)

 rstan_options(auto_write = TRUE)
 options(mc.cores = parallel::detectCores())

flex_behav<-read.csv('~/Downloads/flex_behav.csv',header=TRUE)
mem_data<-read.csv('~/Downloads/mem_behav.csv')
rl_data<-read.csv('~/Documents/alphabeta.csv',header=0)
```

##Behavioral Learning Model
We ran a generalized mixed effects logit model predicting proportion correct with block. Subjects demonstrated significant learning across the task.  

```{r, echo=TRUE, warning=FALSE,message=FALSE}

flex_behav$block_int<-as.numeric(flex_behav$block)-2.5

mbehav<-glmer(correct~block_int+(block_int|subject),data=flex_behav,weights=weights,family=binomial)

summary(mbehav)
```

##Effect of Flexibility on Reinforcement Learning
###Striatal flexibility- REML
We fit a mixed effects generalized linear model using a REML approximation to associate individual learning performance with striatal flexibility across blocks, using lme4.

```{r, echo=TRUE, warning=FALSE,messages=FALSE}
mlearn_str<-glmer(correct~str_flex+(str_flex || subject),data=flex_behav,weights=weights,family=binomial)

summary(mlearn_str)

flex_behav$str_flex_mean<-rep(tapply(flex_behav$str_flex,flex_behav$subject,mean),each=4)
mlearn_str_mean<-glmer(correct~str_flex+str_flex_mean+(str_flex || subject),data=flex_behav,weights=weights,family=binomial)
summary(mlearn_str_mean)
```


###Striatal flexibility- Bayesian model
For appropriate posterior inference, we fit the same model using Hamiltonian Monte Carlo to generate a full posterior distribution for the effect of striatal flexibility on learning performance. 

```{r, echo=TRUE, warning=FALSE,message=FALSE}
options(mc.cores = parallel::detectCores())
flex_behav$numcorr<-as.integer(flex_behav$correct*flex_behav$weights)

mlearn_str_stan<-brm(numcorr~str_flex+(str_flex|subject),data=flex_behav,family=binomial)

summary(mlearn_str_stan)

plot(mlearn_str_stan)
```

###Whole-brain flexibility
Because a global measure of flexibility has also been shown to relate to a number of cogitive processes (Bassett et al 2011, Braun et al 2015), we fit another mixed-effects model with this whole-brain metric as a predictor. 

```{r, echo=TRUE, warning=FALSE,message=FALSE}
mlearn_wb<-glmer(correct~wb_flex+(wb_flex || subject),data=flex_behav,weights=weights,family=binomial)

summary(mlearn_wb)


```